Towards Transparency and Open Science

### 2023-01-24 manuscript.Rmd
update

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: true
    number_sections: false
    keep_tex:  true
header-includes: |
  \usepackage{libertine}
  %\usepackage{ebgaramond}
  %\usepackage{garamondlibre}
  %\usepackage{CormorantGaramond}
  %\usepackage{MinionPro}
  \usepackage{pdfpages}

@@

@@

  \usepackage{polyglossia}
  \setmainlanguage[]{english}
  \setotherlanguage[]{german}
fontsize: 11.5pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
geometry: "left=4cm, right=4cm, top=3.5cm, bottom=4.5cm, bindingoffset=5mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}English:', readLines('abstract.md'), '\\\\par Deutsch:\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  files:
    - abstract.md
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---

>>>>

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    latex_engine: "lualatex"
    toc: true
    number_sections: false
    keep_tex:  true
header-includes: |
  \usepackage{libertine}
  %\usepackage{ebgaramond}
  %\usepackage{garamondlibre}
  %\usepackage{CormorantGaramond}
  %\usepackage{MinionPro}
  \usepackage{pdfpages}

@@

  %https://arthur.maheo.net/beautifying-latex-paper-with-practical-typography/
  \SetTracking{
    encoding={OT1,T1,T2A,LY1,OT4,QX,T5,TS1,EU1,EU2,TU}, }{1000}

@@

  \usepackage{polyglossia}
  \setmainlanguage[]{english}
  \setotherlanguage[]{german}
fontsize: 11pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
geometry: "left=4cm, right=4cm, top=3.5cm, bottom=4.5cm, bindingoffset=5mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}English:', readLines('abstract.md'), '\\\\par Deutsch:\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  files:
    - abstract.md
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---
